Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-16 manuscript/letter.tex

For geophysical purposes, there are three important Terrestrial Reference Systems used in gravity modelling.
They rotate with the Earth and are used for describing
positions and movements of objects on and close to the Earth’s surface
\citep{torge2012}.

The first one is a geocentric system of Cartesian coordinates having
the $Z$-axis coincident with the mean Earth's rotational axis,
the $X$-axis pointing to the Greenwich meridian and the $Y$-axis
directed so as to obtain a right-handed system (Fig. \ref{fig:GCS-GGS}).
This reference system can be found in the literature with different names: Mean Terrestrial System \citep[e.g.,][]{soler1976}, Earth-fixed geocentric Cartesian system \citep[e.g.,][]{torge2012}
or Earth-centered Earth-fixed system \citep[e.g.,][]{bouman_etal2013}, for example. Here, we opted for simply using the term Geocentric Cartesian System (GCS).

Another important reference system is a geocentric system of
geodetic coordinates, which is defined by the reference ellipsoid
used in the Normal Earth model \citep{heiskanen-moritz1967, soler1976,
torge2012, bouman_etal2013}.
In this coordinate system, the position of a point
is defined by the \textit{geometric height} $h$,
\textit{geodetic latitude} $\varphi$ and \textit{longitude} $\lambda$ (Fig. \ref{fig:GCS-GGS}).
For convenience, we call this system Geocentric Geodetic System
(GGS).
At a given point $(h, \varphi, \lambda)$, there are three
mutually-orthogonal unit vectors (Fig. \ref{fig:GCS-GGS}) given by \citep{soler1976}:
\begin{equation}
\hat{\mitbf{u}} =
\begin{bmatrix}
\cos\varphi \, \cos\lambda \\
\cos\varphi \, \sin\lambda \\
\sin\varphi
\end{bmatrix}
\hat{\mitbf{v}} =
\begin{bmatrix}
-\sin\varphi \, \cos\lambda \\
-\sin\varphi \, \sin\lambda \\
\cos\varphi
\end{bmatrix}
\hat{\mitbf{w}} =
\begin{bmatrix}
-\sin\lambda \\
\cos\lambda \\
0
\end{bmatrix} .
\label{eq:unit-vectors}
\end{equation}
The required equations to convert coordinates $(h, \varphi,
\lambda)$ referred to the GGS into coordinates $(X, Y, Z)$ referred to
the GCS (Fig. \ref{fig:GCS-GGS}) and vice versa can be easily found in
the literature \citep[e.g.,][]{heiskanen-moritz1967, torge2012,
bouman_etal2013}.

In local or regional studies, geophysicists commonly use a topocentric
Cartesian coordinate system (TCS) with origin at a point $P$ on or
close to the Earth's surface and axes $x$, $y$ and $z$ (Fig.
\ref{fig:TCS}). In the TCS, the axes $x$ and $y$ are parallel to
the unit vectors $\hat{\mitbf{v}}_{P}$ $\hat{\mitbf{w}}_{P}$, respectively,
whereas the $z$-axis is opposite to the unit vector
$\hat{\mitbf{u}}_{P}$ (eq. \ref{eq:unit-vectors}) and points downward.
Consider, for example, a TCS (Fig. \ref{fig:TCS}) with origin at a point $P$ with
coordinates $(X_{P}, Y_{P}, Z_{P})$ referred to the GCS (Fig. \ref{fig:GCS-GGS}).
In this case, the relationship between the coordinates $(X, Y, Z)$ of a
point in the GCS and the coordinates $(x, y, z)$ of the same point in the
TCS is given by:
\begin{equation}
\begin{bmatrix}
x \\
y \\
z
\end{bmatrix} =
\mitbf{R}^{\top} \begin{bmatrix}
X - X_{P} \\
Y - Y_{P} \\
Z - Z_{P}
\end{bmatrix} \: ,
\label{eq:GCS2TCS}
\end{equation}
where $\mitbf{R}$ is a $3 \times 3$ orthogonal matrix whose
first, second and third columns are defined, respectively,
by the unit vectors $\hat{\mitbf{v}}$, $\hat{\mitbf{w}}$
and $-\hat{\mitbf{u}}$ (eq. \ref{eq:unit-vectors}),
evaluated at the point $P$.

>>>>

For geophysical gravity modelling purposes, there are three important
Terrestrial Reference Systems.
They rotate with the Earth and are used for describing
positions and movements of objects on and close to the Earth's surface
\citep{torge2012}.

The first is a geocentric system of Cartesian coordinates
having the $Z$-axis coincident with the mean rotational axis of the Earth,
the $X$-axis pointing to the Greenwich meridian,
and the $Y$-axis completing a right-handed system (Fig. \ref{fig:GCS-GGS}).
This reference system is called by different names in the literature:
Mean Terrestrial System \citep[e.g.,][]{soler1976},
Earth-fixed geocentric Cartesian system \citep[e.g.,][]{torge2012}
or Earth-centered Earth-fixed system \citep[e.g.,][]{bouman_etal2013},
for example.
Here, we opted for using the term Geocentric Cartesian System (GCS).

The second is a geocentric system of geodetic coordinates
(the Geocentric Geodetic System or GGS),
which is defined by the reference ellipsoid used as the Normal Earth
\citep{heiskanen-moritz1967, soler1976, torge2012, bouman_etal2013}.
The position of a point is defined by
the \textit{geometric height} $h$,
the \textit{geodetic latitude} $\varphi$,
and the \textit{longitude} $\lambda$ (Fig. \ref{fig:GCS-GGS}).
There are also three mutually-orthogonal unit vectors defined at a given point
\citep{soler1976}:

\begin{equation}
    \hat{\mitbf{u}} =
    \begin{bmatrix}
        \cos\varphi \, \cos\lambda \\
        \cos\varphi \, \sin\lambda \\
        \sin\varphi
    \end{bmatrix}
    \hat{\mitbf{v}} =
        \begin{bmatrix}
        -\sin\varphi \, \cos\lambda \\
        -\sin\varphi \, \sin\lambda \\
        \cos\varphi
    \end{bmatrix}
    \hat{\mitbf{w}} =
    \begin{bmatrix}
        -\sin\lambda \\
        \cos\lambda \\
        0
    \end{bmatrix} .
    \label{eq:unit-vectors}
\end{equation}

\noindent Equations for converting between these systems can be found in
the literature \citep[e.g.,][]{heiskanen-moritz1967, torge2012,
bouman_etal2013}.

The third is the Topocentric Cartesian System (TCS),
which is commonly used in local or regional scale geophysical studies.
The origin of the TCS is located at a point $P$,
axes $x$ and $y$ are parallel to
the unit vectors $\hat{\mitbf{v}}$ and $\hat{\mitbf{w}}$
(eq. \ref{eq:unit-vectors}), respectively,
and the $z$-axis is opposite to the unit vector $\hat{\mitbf{u}}$
(Fig. \ref{fig:TCS}).
